SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-06 scipy-1.0/paper.tex
removed subheadings from discussion

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and Astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the code bases, infrastructures, or communities 
is often transferred in some form to the other. At the code
base level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy after the fact.

@@

\fixme{The Discussion should be succinct and must not contain subheadings.}

\subsection*{Impact now}

% While Paul was one of the early adopters at the national laboratories,
% Python's presence is now ubiquitous.

@@

\subsection*{Future Work}

>>>>

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the code bases, infrastructures, or communities 
is often transferred in some form to the other. At the code
base level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy after the fact.

@@

% The Discussion should be succinct and must not contain subheadings.

@@
